The \dealii Library, Version 9.1

### 2019-06-05 9.1/paper.tex
Add punctuation

\dealii version 9.1.0 was released May 21, 2019
This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii software library version 9.1. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.

>>>>

\dealii version 9.1.0 was released May 21, 2019.
This paper provides an
overview of the new features of this major release and serves as a citable
reference for the \dealii software library version 9.1. \dealii is an
object-oriented finite element library used around the world in the
development of finite element solvers. It is available for free under the
GNU Lesser General Public License (LGPL). Downloads are available at
\url{https://www.dealii.org/} and \url{https://github.com/dealii/dealii}.
